Initial Analysis

### 2019-12-24 Initial_Analysis.Rmd
Included RFMO analysis

# UN Regions dataset
UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  group_by(fishing_entity = country_or_area,
           georegion = region_name,
           sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),,
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
  )

@@

# Load and clean transboundary results
Results_Trans <- GetTransResults(Spp)

@@

@@

@@

@@

@@

@@

# Transboundary Species shapefile
World_sf_si <- RFMOs_sf %>%
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_simplify(preserveTopology = TRUE, dTolerance = 0.0001) %>%
  left_join(Transboundary_Spp, by ="eez_name")

ICC <- World_sf_si %>% 
  filter(eez_name == "ICCAT")

# Total catch/Revenue shapefile
World_sf_si_land <- World_land_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1)

@@

# Make map
Plot <- ggplot() +
  geom_sf(data = World_sf_si,
          aes(
            fill =  reorder(Bins_Plot,n_trans_spp),
            colour = reorder(Bins_Plot,n_trans_spp)
          ), 
          size = 0.1
          ) + # n_trans_spp or Bins
  # geom_sf(data = World_sf_si_land) +
  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                  "#00A08A",#"#00A08A", #green
                                  "#F2AD00",#"#F2AD00", # Yellow
                                  "#F98400",#"#F98400", #Orange
                                  "#FF0000"#,"#FF0000" #Red
  ),
  na.value = "grey"
  ) +
  scale_colour_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                    "#00A08A",#"#00A08A", #green
                                    "#F2AD00",#"#F2AD00", # Yellow
                                    "#F98400",#"#F98400", #Orange
                                    "#FF0000"#,"#FF0000" #Red
  ),
  na.value = "grey"
  ) +
  ggtheme_map() +
  facet_wrap(~eez_name)

Plot_Name <- paste("RFMO_100_25_Bins_facet.png", sep = "")

@@

@@

>>>>

# UN Regions dataset
UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  group_by(fishing_entity = country_or_area,
           georegion = region_name,
           sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
  )

@@

# Load and clean transboundary results
# Results_Trans <- GetTransResults(Spp)

@@

### RFMO species list

RFMO_Species <- read.csv(paste(Data_Path,"Spatial_Data/RFMO/clean_rfmos.csv", sep ="")) %>% 
  clean_names() %>% 
  left_join(Exploited_Species,
            by = c("taxon_name"))

# The path
path_world <- paste(Data_Path,"/Spatial_Data/","RFMO","/SAU_RFMO",sep="")
# #The File
fnam_world <- "SAU_RFMO_Sept_2015.shx"
# #Load it!
# 
RFMOs_sf <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world)) %>% 
  dplyr::rename(Name = RFMO_nm_s) %>% 
  st_set_crs(3832) %>% # Making sure is same proyection
  st_transform(3832) # to match shapefiles

Clean_Results_Trans <- Clean_Results_Trans %>% 
  filter(taxon_key %in% RFMO_Species$taxon_key)

@@

length(unique(Tresholded_T_Data$eez_name))

@@

####  Data for Jessica

# Data per Territory
# Transboundary_Jess <- Tresholded_T_Data %>% 
#   group_by(fishing_entity) %>% 
#   summarise(
#     n_trans_spp = length(unique(taxon_key)),
#     # n_neighbours = length(unique(nt_fishing_entity)),
#     # trans_Rrate = n_trans_spp/n_neighbours
#   )

# write_csv(Transboundary_Jess,
#           "transboundary_species_dec19.csv")

@@

### Total from the top 5

Top5 <- c("Peru", "Russian Federation", "Chile", "USA","China")

Total_PeRu <- Revenue_Country %>% 
  filter(fishing_entity %in% PeRu) %>% 
  select(1:2) %>% 
  group_by() %>% 
  summarise(sum(Total_USD)) %>% 
  pull()/79745

@@

lenght(unique(Clean_Results_Transboundary$taxon_key))

Transboundary_Spp %>% 
  ggplot() +
  geom_bar(
    aes(
      x = reorder(eez_name,-n_trans_spp),
      y = n_trans_spp
    ),
    stat = "identity"
  ) +
  coord_flip()

@@

# Transboundary Species shapefile
World_sf_si <- RFMOs_sf %>%
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="eez_name")

# ICCAT <-World_sf_si %>% 
#   filter(eez_name == "ICCAT")
#

# Total catch/Revenue shapefile
World_sf_si_land <- World_land_sf %>%
  st_transform(crs = 4326) #%>% # 4326
  # st_simplify(preserveTopology = TRUE, dTolerance = 0.1)

@@

# Make map
Plot <- ggplot() +
  geom_sf(data = World_sf_si_land) +
  geom_sf(data = World_sf_si,
          aes(
            fill =  n_trans_spp#,
            # colour = reorder(Bins_Plot,n_trans_spp)
          ), 
          size = 0.1
          ) + # n_trans_spp or Bins
  # geom_sf_label(data = World_sf_si,
  #               aes(label = eez_name)
  #               ) +
  scale_fill_gradientn("Number of Shared Species",
    colours = wes_palette("Zissou1", 100, type = "continuous")) +
  # scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
  #                                 "#00A08A",#"#00A08A", #green
  #                                 "#F2AD00",#"#F2AD00", # Yellow
  #                                 "#F98400",#"#F98400", #Orange
  #                                 "#FF0000"#,"#FF0000" #Red
  # ),
  # na.value = "grey"
  # ) +
  # scale_colour_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
  #                                   "#00A08A",#"#00A08A", #green
  #                                   "#F2AD00",#"#F2AD00", # Yellow
  #                                   "#F98400",#"#F98400", #Orange
  #                                   "#FF0000"#,"#FF0000" #Red
  # ),
  # na.value = "grey"
  # ) +
  ggtheme_map()

Plot_Name <- paste("RFMO_100_25.png", sep = "")

@@

# Number of coastal nations
length(unique(Status_Data_Plot$individual))

@@

## Statistics on species

```{r Spp_Stats, eval = T, echo = F}

head(Species_Data)

# Differences between groups
Stat_spp_aov <- aov(value~group, data = Species_Data)
Stat_spp_aov
summary(Stat_spp_aov)
# Df Sum Sq Mean Sq F value   Pr(>F)    
# group         5  24836    4967   14.67 5.52e-11 *** (YUP)
# Residuals   109  36915     339

TukeyHSD(Stat_spp_aov)
